ray

### 2022-03-19 outputs/paper/ray.Rmd
age groups for first born

```{r}
first_born <- raw_data %>% select(c(hlthmntl, agekdbrn)) %>% filter(!is.na(agekdbrn), !is.na(hlthmntl)) %>%
  mutate(born = case_when(
    agekdbrn <= 18 ~ "1",
    agekdbrn <= 25 ~ "2",
    agekdbrn <= 30 ~ "3",
    agekdbrn <= 40 ~ "4",
    agekdbrn <= 50 ~ "5",
    agekdbrn > 50 ~ "6",

>>>>

```{r}
first_born <- raw_data %>% select(c(hlthmntl, agekdbrn)) %>% filter(!is.na(agekdbrn), !is.na(hlthmntl)) %>%
  mutate(born = case_when(
    agekdbrn < 18 ~ '< 18',
    agekdbrn >= 18 & agekdbrn <= 29 ~ '18-29',
    agekdbrn >= 30 & agekdbrn <=39~ '30-39',
    agekdbrn >= 40 & agekdbrn <=49~ '40-49',
    agekdbrn >= 50 & agekdbrn <=64~ '50-64',
    agekdbrn >= 65 & agekdbrn <=89~ '65-89'
